\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Problem Set 1}
\author{y.mozaffar }
\date{January 2020}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section{Introduction}
I am primarily interested in industrial organization within the field of Economics. As with any/all disciplines within econ, IO is increasingly reliant on data in its research. After completing my degrees in Economics, I plan to go to law school, but that doesn't mean I'm leaving Economics behind. I'm not sure exactly where my legal career will take me, but I know for sure that I want it to include elements of Economics. Options include labor law, consumer protection, other types of corporate regulations, etc. There is a growing demand for more technocratic lawyers, particularly in legal scholarship, so having graduate-level coursework in Economics and Data Science will serve me really well in the legal field. 
For my class project, I'm intending to use my independent graduate research project, which I'm beginning to work on now. The project deals with the various factors that may result in the formation of a monopoly, whether that be market conditions, legal intervention, etc, with the ultimate goal of attempting to create a model that predicts when a firm/industry is likely to become monopolistic. I'm also planning on submitting a "pilot version" of the paper to a conference in March, which may be a case study to glean some insight into the viability of my models before proceeding with the project. 



\section{Equation}
\[a^2+b^2=c^2\]


\end{document}
